Estimating Information Transfer in Hard Parameter Sharing via Precise Bias-variance Asymptotics

### 2021-07-17 revision_journal/results.tex
finish sec 4

>>>>

Consider the special case with $\Sigma^{(2)}=\id$, $a=1$ and the random effect model. Let $\sigma_i^{(1)}$ be the eigenvalues of $\Sigma^{(1)}$. Define the function 
\be\label{g1new} g_0(x)= \frac{1}{n_1}\sum_{i=1}^p \frac{\sigma_i^{(1)}}{1+ \sigma_i^{(1)} x} -\frac{1}{x} .\ee
Let $y$ be the unique positive solution to the equation 
\be\nonumber
\frac{n_1+n_2-p}{n_1} + g_0(y) \cdot \left( 1+    y\right)=0 .
\ee
Define the following three functions of $y$:
$$f_1= \frac{n_1}{p}y + \frac{n_1-p}{p}\frac1{g_0(y)},\quad f_2= \frac{n_1}{p}\frac{1}{g_0'(y)}- \frac{n_1-p}{p}\frac1{[g_0(y)]^2},\quad f_3= - g_0(y),$$
where $g_0'(y)$ is the derivative
$$ g_0'(y)=  -\frac{1}{n_1}\sum_{i=1}^p \frac{(\sigma_i^{(1)})^2}{(1+ \sigma_i^{(1)} y)^2} +\frac{1}{y^2}. $$
Then the variance limit is given by
$$ L_{\var}(1)=\sigma^2 \frac{p}{n_1}f_1,$$
and the bias limit is given by 
$$ L_{\bias}(1)=2\mu^2 \frac{1 - 2f_1 f_3  +f_2 f_3^2  }{ 1 - \frac{p}{n_2}f_2 f_3^2 }.$$
(Here $2\mu^2$ represents $\|\beta^{(1)}-\beta^{(2)}\|^2$.)
